\vspace{2cm} \LARGE \bf Seasonal influenza circulation patterns and projections for 2016-2017

### 2016-09-17 auspice/reports/tex/sep-2016.tex
Fix typos in Sep report.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H3N2_mutations.png}
	\caption{\textbf{Frequency trajectories of 3c2.a subclades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Sep 1 2016.
	}
	\label{H3N2_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/H1N1pdm_clades.png}
	\caption{\textbf{Frequency trajectories of H1N1pdm clades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Sep 1 2016.
	}
	\label{H1N1pdm_clades}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/Yam_clades.png}
	\caption{\textbf{Frequency trajectories of B/Yam clades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Sep 1 2016.
	}
	\label{Yam_clades}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\textwidth]{../figures/sep-2016/Yam_tree.png}
	\caption{\textbf{H3N2 phylogeny colored by genotype.}
	}
	\label{Yam_tree}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/feb-2016/Yam_mutations.png}
	\caption{\textbf{Frequency trajectories of B/Yam variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Sep 1 2016.
	}
	\label{Yam_mutations}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/sep-2016/H3N2_mutations.png}
	\caption{\textbf{Frequency trajectories of 3c2.a subclades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Sep 1 2016.
	}
	\label{H3N2_mutations}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/sep-2016/H1N1pdm_clades.png}
	\caption{\textbf{Frequency trajectories of H1N1pdm clades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Sep 1 2016.
	}
	\label{H1N1pdm_clades}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/sep-2016/Yam_clades.png}
	\caption{\textbf{Frequency trajectories of B/Yam clades.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Sep 1 2016.
	}
	\label{Yam_clades}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\textwidth]{../figures/sep-2016/Yam_tree.png}
	\caption{\textbf{B/Yam phylogeny colored by genotype.}
	}
	\label{Yam_tree}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{../figures/sep-2016/Yam_mutations.png}
	\caption{\textbf{Frequency trajectories of B/Yam variants.}
	We estimate frequencies of different clades based on sample counts and collection dates.
	We use a Brownian motion process prior to smooth frequencies from month-to-month.
	Transparent bands show an estimate the 95\% confidence interval based on sample counts.
	The final point represents our frequency estimate for Sep 1 2016.
	}
	\label{Yam_mutations}
\end{figure}
